Results

### 2025-06-20 notebooks/00_index.qmd
fig: update

tselect(A, t) = A[Ti(Near(t))]
function tselect(A, t, δt)
    tmp = @views A[Ti((t - δt) .. (t + δt))]
    length(tmp) == 0 ? missing : tmp[Ti(Near(t))]
end

@@

f = Figure(; size=(1200, 800))
psp_event = filter_low_mva_quality(psp_df)[4, :]
res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
@info "v_l_ratio" psp_event.v_l_ratio
# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_config)
# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_config, Second(10))
f

@@

update_theme!(;
    figure_padding=1,
    fonts=(; regular=AoG.firasans("Regular"), bold=AoG.firasans("Medium")),
    Legend=(; framevisible=false, padding=(0, 0, 0, -15)),
    Axis=(; xlabelfont=:bold, ylabelfont=:bold),
)

@@

tvars_psp = [psp_B, psp_n, psp_V]
tvars_psp_all = [
    psp_B,
    set(PSP.n; ylabel=𝒀.n),
    psp_V,
    set(PSP.T; ylabel=𝒀.T)
]
```

```{julia}
wind_B = set(tnorm_combine ∘ Wind.B_GSE_1MIN; ylabel=𝒀.B, labels=𝑳.B_XYZ)
wind_V = replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=𝒀.V, labels=𝑳.V_XYZ)
wind_n = set(Wind.n_p_K0; ylabel=𝒀.n, yscale=identity)

tvars_wind = [wind_B, wind_n, wind_V]
tvars_wind_all = [
    wind_B,
    set(Wind.n; ylabel=𝒀.n),
    wind_V,
    set(Wind.T; ylabel=𝒀.T)
]
```

```{julia}
using Intervals: Interval

function get_themis_tmask(t0, t1)
    thx_v_gse = THEMIS.V_GSE(t0, t1)
    _times = @views SPEDAS.times(thx_v_gse)[(thx_v_gse[:, 1].>-200u"km/s").|(thx_v_gse[:, 2].<-50u"km/s")]
    dt = Minute(10)
    its = union([Interval(t - dt, t + dt) for t in _times])
    return tmask!(its)
end
```

@@

function get_vl_ratio_ts(df)
    vl_ratio_ts1 = DimArray(df.v_l_ratio, Ti(df.time))
    vl_ratio_ts2 = DimArray(df.v_l_ratio_Λ, Ti(df.time))
    gfunc = x -> floor(x, Hour(4))
    vl_ratio_ts = hcat(
        nanmedian.(disallowmissing.(groupby(vl_ratio_ts1, Ti => gfunc))),
        nanmedian.(disallowmissing.(filter.(!ismissing, groupby(vl_ratio_ts2, Ti => gfunc))))
    )
    set_meta!(vl_ratio_ts; ylabel=L"R_{VB}", labels=["Isotropy", "Anisotropy"])
    return vl_ratio_ts
end
```

```{julia}
update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(1, 1, 1, 15))

@@

function modify_faxs_base!(faxs)
    B_ax = faxs.axes[1]
    B_ax.ylabel[] = 𝒀.B
    n_ax = faxs.axes[2]
    n_ax.yscale[] = identity
    n_ax.ylabel[] = 𝒀.n
    V_ax = faxs.axes[3]
    V_ax.ylabel[] = 𝒀.V
end

function modify_faxs_vl!(faxs)
    ylims!(faxs.axes[end-1], 0.09, 0.85)
    faxs.axes[4].ylabel[] = "T (eV)"
    β_ax = faxs.axes[6]
    β_ax.yscale[] = log10
    β_ax.ylabel[] = "β"
    ylims!(β_ax, 8e-2, 4e1)
end

@@

        B = set_meta!(PSP.B_1MIN(tmin_psp, tmax_psp); labels=𝑳.B_RTN)
        V = set_meta!(psp_V(tmin_psp, tmax_psp); labels=𝑳.V_RTN)
        n = PSP.n_spi(tmin_psp, tmax_psp)
        T = PSP.pTemp(tmin_psp, tmax_psp; add_unit=false)

@@

        psp_v_l_ratio_ts = get_vl_ratio_ts(psp_df)
        tvars_psp = (tnorm_combine(B), n, V, [T, Tp, Te], psp_v_l_ratio_ts, β)

        Wind_Tp2 = Wind.pTemp_T2(tmin_wind, tmax_wind)
        Wind_Te2 = Wind.eTemp_T2(tmin_wind, tmax_wind)
        add_temp_anisotropy!(wind_df, Wind_Tp2, Wind_Te2, Minute(2))
        compute_anisotropy_params!(wind_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))

        B = Wind.B_GSE_1MIN(tmin_wind, tmax_wind)
        n = Wind.n_p_K0(tmin_wind, tmax_wind) |> tsort
        T = rebuild(Wind.T_p_PLSP(tmin_wind, tmax_wind) |> tsort; metadata=(; labels=[L"T_p"]))
        B_mag = tnorm(B)
        β = Discontinuity.plasma_beta.(tsync(T, n, B_mag)...)

        wind_v_l_ratio_ts = get_vl_ratio_ts(wind_df)
        tvars_wind = (tvars_wind..., [T, Wind.Temp_ani[1:2]...], wind_v_l_ratio_ts, β)
    end

    faxs = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
    modify_faxs_base!(faxs)
    plot_vl_ratio && modify_faxs_vl!(faxs)
    add_labels!(f[1, 1]; labels, open="(a.", padding)
    faxs = tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
    modify_faxs_base!(faxs)
    plot_vl_ratio && modify_faxs_vl!(faxs)
    add_labels!(f[1, 2]; labels, open="(b.", padding)
    # _tmask! = get_themis_tmask(tmin_wind, tmax_wind)
    # tplot(f[1, 3], _tmask! .∘ tvars_themis[1:3], tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 3]; labels, open="(c.")
    easy_save(fname; formats=(:pdf,))
    display(f)

@@

>>>>

@@

f = Figure(; size=(1200, 800))
psp_event = filter_low_mva_quality(psp_df)[5, :]
res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
@info "v_l_ratio" psp_event.v_l_ratio
# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_config)
# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_config, Second(10))
f

@@

update_theme!(;
    figure_padding=1,
    fonts=(; regular=AoG.firasans("Regular"), bold=AoG.firasans("Medium")),
    Legend=(; framevisible=false, padding=(0, 0, 0, -15)),
    Axis=(; xlabelfont=:bold, ylabelfont=:bold),
)
```

@@

wind_B = set(tnorm_combine ∘ Wind.B_GSE_1MIN; ylabel=𝒀.B, labels=𝑳.B_XYZ)
wind_V = replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=𝒀.V, labels=𝑳.V_XYZ)
wind_n = set(Wind.n_p_K0; ylabel=𝒀.n, yscale=identity)
```

@@

function get_vl_ratio_ts(df, col, dt::TimePeriod=Hour(4))
    data = getproperty(df, col)
    vl_ratio_ts = DimArray(data, Ti(df.time))
    gfunc = x -> floor(x, dt)
    gdf = groupby(vl_ratio_ts, Ti => gfunc)
    vl_ratio_ts_m = nanmedian.(disallowmissing.(filter.(!ismissing, gdf)))
    n = rebuild(length.(gdf); metadata=(; ylabel="N (#)", plottype=:Stairs))
    set_meta!(vl_ratio_ts_m; ylabel=L"R_{VB}", labels=["Isotropy", "Anisotropy"], plottype=:Stairs)
    return vl_ratio_ts_m, n
end

function get_vl_ratio_ts(df, dt::TimePeriod=Hour(4))
    v_l_ratio_ts, n1 = _get_vl_ratio_ts(df, :v_l_ratio, dt)
    v_l_ratio_Λ_ts, n2 = _get_vl_ratio_ts(df, :v_l_ratio_Λ, dt)
    vl_ratio_ts = hcat(v_l_ratio_ts, v_l_ratio_Λ_ts)
    return vl_ratio_ts, n1
end
```

```{julia}
using SPEDAS: tvec
using CairoMakie
CairoMakie.activate!()

update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(1, 1, 1, 15))

@@

function modify_faxs_base!(faxs)
    B_ax = faxs.axes[1]
    B_ax.ylabel[] = 𝒀.B
    V_ax = faxs.axes[3]
    V_ax.ylabel[] = 𝒀.V
    n_ax = faxs.axes[2]
    n_ax.yscale[] = identity
    n_ax.ylabel[] = 𝒀.n
end

function modify_faxs_vl!(faxs)
    T_ax = faxs.axes[end-3]
    T_ax.ylabel[] = "T (eV)"

    R_ax = faxs.axes[end-1]
    ylims!(R_ax, 0.09, 0.85)

    β_ax = faxs.axes[end]
    β_ax.yscale[] = log10
    β_ax.ylabel[] = "β"
    ylims!(β_ax, 8e-2, 4e1)
end

@@

        B = set_meta!(PSP.B_1MIN(tmin_psp, tmax_psp); labels=𝑳.B_RTN)
        V = set_meta!(psp_V(tmin_psp, tmax_psp); labels=𝑳.V_RTN)
        n = PSP.n_spi(tmin_psp, tmax_psp) |> tvec
        T = PSP.pTemp(tmin_psp, tmax_psp; add_unit=false) |> tvec

@@

        psp_v_l_ratio_ts, psp_count = get_vl_ratio_ts(psp_df)
        tvars_psp = (B_mag, n, tnorm(V), tmean.((T, Tp, Te), Minute(8)), psp_count, psp_v_l_ratio_ts, β)

        Wind_Tp2 = Wind.pTemp_T2(tmin_wind, tmax_wind; add_unit=false)
        Wind_Te2 = Wind.eTemp_T2(tmin_wind, tmax_wind; add_unit=false)
        add_temp_anisotropy!(wind_df, Wind_Tp2, Wind_Te2, Minute(2))
        compute_anisotropy_params!(wind_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))

        B = Wind.B_GSE_1MIN(tmin_wind, tmax_wind)
        V = wind_V(tmin_wind, tmax_wind)
        n = Wind.n_p_K0(tmin_wind, tmax_wind) |> tsort
        T = rebuild(Wind.T_p_PLSP(tmin_wind, tmax_wind; add_unit=false) |> tsort; metadata=(; labels=[L"T_p"]))
        B_mag = tnorm(B)
        β = Discontinuity.plasma_beta.(tsync(T, n, B_mag)...)

        wind_v_l_ratio_ts, wind_count = get_vl_ratio_ts(wind_df)
        tvars_wind = (B_mag, n, tnorm(tsort(V)), [T, Wind_Tp2, Wind_Te2], wind_count, wind_v_l_ratio_ts, β)
    end

    faxs = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
    modify_faxs_base!(faxs)
    plot_vl_ratio && modify_faxs_vl!(faxs)
    add_labels!(f[1, 1]; labels, open="(a.", padding)
    faxs = tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
    modify_faxs_base!(faxs)
    plot_vl_ratio && modify_faxs_vl!(faxs)
    add_labels!(f[1, 2]; labels, open="(b.", padding)

    # _tmask! = get_themis_tmask(tmin_wind, tmax_wind)
    # tplot(f[1, 3], _tmask! .∘ tvars_themis[1:3], tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 3]; labels, open="(c.")

    easy_save(fname; formats=(:pdf,))
    display(f)

@@

## The effect of tau

```{julia}
psp_df_taus = map([8, 16, 32]) do tau
    psp_config["tau"] = tau
    df = PSPAnisotropy.produce(psp_config)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end

wind_df_taus = map([8, 16, 32]) do tau
    wind_config["tau"] = tau
    df = PSPAnisotropy.produce(wind_config)
    @transform! df :tau = tau
    compute_Alfvenicity_params!(df)
end
```

```{julia}
f = Figure()
axR1 = Axis(f[1, 1])
axn1 = Axis(f[2, 1])
for (i, df) in enumerate(psp_df_taus)
    v_l_ratio_ts, n = get_vl_ratio_ts(df, :v_l_ratio)
    lines!(axR1, v_l_ratio_ts)
    lines!(axn1, n)
end

axR2 = Axis(f[1, 2])
axn2 = Axis(f[2, 2])
for (i, df) in enumerate(wind_df_taus)
    v_l_ratio_ts, n = get_vl_ratio_ts(df, :v_l_ratio)
    lines!(axR2, v_l_ratio_ts)
    lines!(axn2, n)
end

ylims!.((axR1, axR2), 0.2, 0.8)
ylims!.((axn1, axn2), 11, 121)
easy_save("vl_ratio-tau")
f
```
